---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 7, 2019"
output: html_document
---

# Base R

## Data Types

1. Numeric (Double)
    + Can include integers and decimal numbers (continuous variables)
    + __EXAMPLE:__
```{r}
is.numeric(c(1, 2, 3.5, 6.7))
is.numeric(c(1, 2, 3, 6))
is.numeric(c(TRUE, FALSE, TRUE))
is.numeric(c("a", 2, 3, 6))
is.numeric(c("a", "b", "c", "d"))
```

2. Integer
   + Only whole numbers (discrete variables)
   + Generally, R will store vectors of integers as type Numeric
   + From `is.integer()`help file: "is.integer(x) does not test if x contains integer numbers!"
   + __EXAMPLE:__
```{r}
is.integer(c(1, 2, 3.5, 6.7))
is.integer(c(1, 2, 3, 6))
is.integer(c(TRUE, FALSE, TRUE))
is.integer(c("a", 2, 3, 6))
is.integer(c("a", "b", "c", "d"))
```

3. Logical 
    + TRUE or FALSE values
    + __EXAMPLE:__
```{r}
is.logical(c(1, 2, 3.5, 6.7))
is.logical(c(1, 2, 3, 6))
is.logical(c(TRUE, FALSE, TRUE))
is.logical(c("a", 2, 3, 6))
is.logical(c("a", "b", "c", "d"))
```
4. Character
    + Alphanumeric
    + __EXAMPLE:__
```{r}
is.character(c(1, 2, 3.5, 6.7))
is.character(c(1, 2, 3, 6))
is.character(c(TRUE, FALSE, TRUE))
is.character(c("a", 2, 3, 6))
is.character(c("a", "b", "c", "d"))
```

5. Factor
    + A special integer vector to assign order
    + __Use:__ assign custom order to categorical variables
        + If you were to sort a character vector, R would sort the vector alphabetically.
    + __EXAMPLE:__
```{r}
is.factor(c(1, 2, 3.5, 6.7))
is.factor(c(1, 2, 3, 6))
is.factor(c(TRUE, FALSE, TRUE))
is.factor(c("a", 2, 3, 6))
is.factor(c("a", "b", "c", "d"))
```
    
Example of sorting a character vector.
```{r}
char.vec <- c("a", "b", "c", "d")
sort(char.vec)
```
    
Example of sorting a factor vector.
```{r}
factor.vec <- factor(c("a", "b", "c", "d"),
                     levels = c("d", "a", "c", "b"))
sort(factor.vec)
as.numeric(factor.vec)
```

