---
title: "Untitled"
author: "Zachary M. Smith"
date: "September 22, 2018"
output: html_document
---

# Quick Reference

1. Cheat Sheets: https://www.rstudio.com/resources/cheatsheets/
2. R Bloggers: https://www.r-bloggers.com/
3. Questions
    + StackOverflow: https://stackoverflow.com
    + R Community: https://community.rstudio.com/
4. Style Guides
    + Hadely Wickham: http://style.tidyverse.org/index.html
    + Google: https://google.github.io/styleguide/Rguide.xml
5. Books and Papers
    + R for Data Science: http://r4ds.had.co.nz/
    + Advanced R: http://adv-r.had.co.nz/
    + R Packages: http://r-pkgs.had.co.nz/
    + Tidy Data: https://www.jstatsoft.org/article/view/v059i10
6. Packages
    + Shiny (Interactive Apps): https://shiny.rstudio.com/
        + Tutorials: https://shiny.rstudio.com/tutorial/
    + Leaflet (Interactive Maps): https://rstudio.github.io/leaflet/
    + DT (Interactive Tables): https://rstudio.github.io/DT/
    + Dygraphs (Interactive Time Series Plots): https://rstudio.github.io/dygraphs/
    + Plotly (Interactive Plots): https://plot.ly/r/
    + Tidyverse Packages (Ecosystem of Packages): https://www.tidyverse.org/
    + Rmarkdown (Documentation): https://rmarkdown.rstudio.com/lesson-1.html
    + USGS GitHub: https://github.com/USGS-R
        + dataRetrieval (Acquire data from the Water Quality Portal): https://cran.r-project.org/web/packages/dataRetrieval/vignettes/dataRetrieval.html
        + EGRET (Analysis of long-term changes in water quality and streamflow): https://cran.r-project.org/web/packages/EGRET/vignettes/EGRET.pdf

## Installation Links

```{r, echo=FALSE}
urls <- c("https://cran.r-project.org/bin/windows/base/",
          "https://www.rstudio.com/products/rstudio/download/#download",
          "https://git-scm.com/downloads")
link.df <- data.frame(
  Software = c("R", "R Studio", "Git"),
  Link = paste0("[", urls, "](", urls, ")")
)

knitr::kable(link.df)
```

## Updating Software and Packages

### R

Run the following code in the R GUI (code copied from: https://www.r-statistics.com/2013/03/updating-r-from-r-on-windows-using-the-installr-package/). Make sure R Studio is closed.

```{r, eval=FALSE}
# installing/loading the package:
if(!require(installr)) {
install.packages("installr");
require(installr)
} #load / install+load installr

# using the package:
updateR()
```

### RStudio

In RStudio -> Help -> Check for Updates -> follow instructions

### R-Packages

In RStudio -> Tools -> Check for Package Updates… - > follow instructions 
