---
title: "Untitled"
author: "Zachary M. Smith"
date: "September 23, 2018"
output: html_document
---

# Tidyverse

The tidyverse is an ecosystem of packages that work well together and often make it easier to deal with data in R. 


## Tidyverse Directory

1. Data Manipulation
    + [dplyr]
    + [tidyr]
2. Loops
    + [purrr]
3. Visualization
    + [ggplot2]
4. Dates
    + [lubridate]
5. Strings
    + [stringr]
6. Factors
    + [forcats]
7. Import Data
    + [readr]
    + [readXl]

## Pipe Opperator (%>%)

I often find that the pipe operator, %>%, from the magrittr package is confusing to those unfamiliar with the tidyverse, and right fully so. It takes a little while to wrap your head around the pipe operator but once you do I think you will find its use makes R code more legible. In essence base R works from the inside-out, while the pipe operator presents the code in a linear fashion. For example, imagine you have a character vector x and you want to trim leading/trailing white space, then keep only unique strings, and then make all characters lowercase. In base R, the code would look this:
```{r, eval=TRUE}
tolower(unique(trimws(x)))
```

Again, base R works from the inside-out, so first trimws() is used to remove leading/trailing white space, then unique() is used to remove duplicate strings, and finally tolower() is used to convert all characters to lowercase. Using the pipe operator, the code would look like this:
```{r, eval=TRUE}
x %>% 
  trimws() %>% 
  unique() %>% 
  tolower()
```

The pipe operator presents the functions in the order you intend them to be performed; therefore, the code should be easier to read and more intuitive, which should in turn reduce errors. For more information on the pipe operator please refer to http://magrittr.tidyverse.org/.

## dplyr



## tidyr



## stringr



## lubridate



## purrr



## ggplot2



## tibble



## forcats



## readr

The tidyverse package developed for importing C

## readXl




